### 2021-09-27 博士/论文提交/adversarial_attack/TCSVT/大修/response/response.tex

% 消融实验：噪声攻击。
(4) We have added a new experiment to evaluate the attack performance of the random patterns.

% 消融实验
(5) We have added a new experiment to evaluate the attack performance when only adding the perturbation to the search/template image.

% 引用论文
(6) We have added 3 papers published in the IEEE Transactions on Circuits and Systems for Video Technology, which are most closely related to our manuscript, and analysed what is distinctive / new about our current manuscript related to these previously published papers. For your convenience in cross-checking, the new text is given as follows.

\uline{
Some recent research topics which are mostly related to adversarial attack also include digital watermarking [33], 3D face presentation attacks to the face recognition networks [34] and adversarial defense for image classifiers [26].
% Xiong et. al. [33] propose to generate the digital watermarking by slightly modifying the pixel values of video frames to protect video content from unauthorized access. Compared with [33], our purpose of modifying pixel values of video frames is attacking the tracker, instead of detecting the illegal distribution of a digital movie.
% Jia et. al. [34] propose to generate 3D face artifacts to attack the face recognition network. Compared with [34], our method directly modifies the input of the network instead of changing the input of cameras using 3D face artifacts.
% Wang et. al. [26] propose the white-box attack/defense methods for image classifiers. Compared with [26], we focus on attacking the object tracking networks instead of the image classification networks.
}

@@

%%%%%%%%%%%%%%%%% 审稿人 1 %%%%%%%%%%%%%%%%%
\newpage
{\centering\section*{Response Letter to Reviewer \#1}}
\noindent Dear Reviewer \#1:

Thank you very much for your thorough review. Your insightful comments are very helpful for us to improve the quality of the paper. According to your comments and suggestions, we have carefully and extensively revised the manuscript. The main revised parts are highlighted by underlines in the underlined version for your convenience. You will find that all your comments and suggestions are considered and followed. We hope that our revised manuscript is now appropriate for publication in IEEE Transactions on Circuits and Systems for Video Technology.
In addition, point-to-point responses to your comments are given below and highlighted using bold font in line with your comments in order to facilitate cross-referencing.\\[10pt]
\indent We are looking forward to your reply.\\[10pt]
\noindent Yours sincerely,\\
\noindent Zhenbang Li, Yaya Shi, Jin Gao, Shaoru Wang, Bing Li, Pengpeng Liang, Weiming Hu
\\
\\
\\
\noindent Dr. Jin Gao (Contact author)\\
\noindent National Laboratory of Pattern Recognition (NLPR)\\
\noindent Institute of Automation, Chinese Academy of Sciences (CASIA)\\
\noindent Address: No. 95, Zhongguancun East Road, Haidian District,\\
\noindent Beijing 100190, P. R. China\\
\noindent Email: jin.gao@nlpr.ia.ac.cn

\newpage
\textit{This paper addresses the task of attacking Siamese network-based trackers in a simple yet effective fashion. Unlike other methods that operate in the video-specific attacking regime (which resides on network inference for generating perturbations while tracking), this method is the first to perform universal targeted attacks for Siamese trackers utilizing both the translucent perturbation and the adversarial patch together. By adding the perturbation to the template and adding the patch to the search image while performing tracking, this work fools the Siamese trackers to the fake target region and thus makes them fail in tracking the real target object. Overall, this is an interesting paper, and it is well written and organized. As it is a resubmitted manuscript, I notice that the authors have made substantial changes to the previous manuscript, which are able to appropriately respond to the comments made by the previous reviewers. Although the template perturbation and adversarial patch are both easy to observe for human eyes as the previous reviewers have pointed out, and the SSIMs for them are also lower than the video-specific attacking method, e.g., FAN [6], this reviewer believes that this proposed new framework can be a new configuration of adversarial attack on visual tracking for its achieved balance between the attack efficiency and the perturbation perceptibility. This new configuration will attract increasing attention from the visual tracking attack community to study on more efficient attack methods.}

@@

\textbf{Sorry for the inconvenience of reading Fig. 9 caused by the small font size.
We are willing to adjust Fig. 9 font size to make it easier to read on the computer, but because we have added many ablation experiments to revised manuscript, the total number of pages exceeds the maximum page limit for TCSVT (i.e., 14 pages). Therefore we have to remove the analysis of the attack performance for each attribute of the OTB as well as Fig. 9.
}

%%%% 问题 1.4 %%%%
\textit{Also, some recent papers are valued to be referred (2020-2021), to enhance the quality.}

\textbf{Thanks for the good comments. We have added several 2020-2021 related papers to enhance the quality of the revised manuscript. For your convenience of cross review, the new text is given as follows.}

\uline{Some recent research topics which are mostly related to adversarial attack also include digital watermarking [33], 3D face presentation attacks to the face recognition networks [34] and adversarial defense for image classifiers [26].
% Xiong et. al. [33] propose to generate the digital watermarking by slightly modifying the pixel values of video frames to protect video content from unauthorized access. Compared with [33], our purpose of modifying pixel values of video frames is attacking the tracker, instead of detecting the illegal distribution of a digital movie.
% Jia et. al. [34] propose to generate 3D face artifacts to attack the face recognition network. Compared with [34], our method directly modifies the input of the network instead of changing the input of cameras using 3D face artifacts.
% Wang et. al. [26] propose the white-box attack/defense methods for image classifiers. Compared with [26], we focus on attacking the object tracking networks instead of the image classification networks.
}

@@

\textit{- On page 4, ‘imperceptible’ $\rightarrow$ ‘imperceptibly’ in line 57.}

\textit{- The reinitialization of VOT-toolkit should be mentioned in the part of ‘experimental setup’.}

\textit{- On page 7, ‘.(see Table I)’ is a typo.}

\textbf{Thanks for the good comment. We have carefully checked through the whole text and corrected the grammar mistakes and typos. Specifically,}
\textbf{We have replaced ``Experiment results on OTB2015 [11], GOT-10k [12], LaSOT [12], UAV123 [13], VOT1016 [14], VOT2018 [15] and VOT2019 [16]. benchmarks demonstrate the effectiveness and efficiency of our approach.'' with}
``\uline{Experiment results on OTB2015 [11], GOT-10k [12], LaSOT [13], VOT2016 [14], VOT2018 [15] and VOT2019 [16] benchmarks demonstrate the effectiveness and efficiency of our approach.}''
\textbf{in Section I of the revised manuscript.}

@@

\textbf{We have replaced ``In SiamFC++, the tracker first transforms the paired reference frame $I_1$ and annotation $b_1^{gt}$ to get an template image $\textbf z_1$, and transforms the search frame $I_i$ to get the search image $\textbf x_i$ centered at the position estimated in the previous frame.'' with}
``\uline{In SiamFC++, the tracker first transforms the paired reference frame $I_1$ and annotation $b_1^{gt}$ to get a template image $\textbf z_1$, and transforms the search frame $I_i$ to get the search image $\textbf x_i$ centered at the position estimated in the previous frame.}''
\textbf{in Section III.A of the revised manuscript.}

\textbf{We have replaced ``However, CNN attacks are usually expected imperceptible but the above method has to paste an obviously noticeable fake target patch to tracking frames, which raises the risk of being suspected.'' with}
``\uline{However, CNN attacks are usually expected to be imperceptible but the above method has to paste an obviously noticeable fake target patch to tracking frames, which raises the risk of being suspected.}''
\textbf{in Section III.A of the revised manuscript.}

\textbf{We have  replaced ``$A_add$ adds the patch into the search image $\textbf x$ at location $(\frac{x_0+x_1}{2},\frac{y_0+y_1}{2})$.'' with}
``\uline{$A_{add}$ adds the patch into the search image $\textbf x$ at location $(\frac{x_0+x_1}{2},\frac{y_0+y_1}{2})$.}''
\textbf{in Section III.B of the revised manuscript.}

\textbf{We have replaced ``We evaluate our video-agnostic perturbations for targeted attacks on several tracking benchmarks, i.e., OTB2015 [11], GOT-10k [12], LaSOT [13], UAV123 [13], VOT1016 [14], VOT2018 [15] and VOT2019 [16].'' with}
``\uline{We evaluate our video-agnostic perturbations for targeted attacks on several tracking benchmarks, i.e., OTB2015 [11], GOT-10k [12], LaSOT [13], VOT2016 [14], VOT2018 [15] and VOT2019 [16].}''
\textbf{in Section IV.A of the revised manuscript.}

\textbf{We have replaced ``We adopt COCO [63], ILSVRC-VID [64] and the training splits of GOT-10k [12] and LaSOT [13] as our training set. (see Table I)'' with}
``\uline{We adopt COCO [63], ILSVRC-VID [64] and the training splits of GOT-10k [12] and LaSOT [13] as our training set.}''
\textbf{in Section IV.B of the revised manuscript.}

@@

%%%% 问题 3.2 %%%%
\textit{2. The proposed method and offline training phase should be explained more clearly. For instance, the termination of offline training or offline optimization is missed affecting perturbation values.}

\textbf{Thanks for the good comment. As suggested, we have explained in detail the perturbation update process in offline training.
The detailed analysis is added in Section III.B of the revised manuscript.
For your convenience in cross-checking, the new text is given as follows.}

\uline{Before introducing our perturbation update process in offline training, we first revisit the popular adversarial example generation methods (\eg,~[55], [56]). One of the simplest methods to generate adversarial image $I^{adv}$ is FGSM~[55] and works by linearizing the loss function around the network weights and obtaining an optimal max-norm constrained perturbation for generating the adversarial image:}
\begin{equation}
    I^{adv} = I + \epsilon \cdot \text{ sign} \bigl( \nabla_I J(I, y_{true})  \bigr),
    \vspace{-0.1cm}
\end{equation}
\uline{where $I$ is the input clean image, and the values of its pixels are integer numbers in the range [0, 255]. $y_{true}$ is the true label for the image $I$, $J(I, y_{true})$ is the cost function for training the neural network, and $\epsilon$ is a hyper-parameter to be chosen. A straightforward way to extend the above method is applying it multiple times with small step size. This leads to Basic Iterative Method (BIM) introduced in [56]:}
\begin{equation}
    \begin{gathered}
        I_0^{adv} = I, \\
        I_{N+1}^{adv} = Clip_{I, \epsilon}\left\{I_N^{adv}+\epsilon \cdot \text{ sign}(\nabla_I J(I_N^{adv},y_{true}))\right\},
    \end{gathered}
\end{equation}
\uline{where the pixel values of intermediate results are clipped after each step to ensure that they are in
an $\epsilon$-neighbourhood of the original image. The BIM method can be easily made into an attacker for a specific desired target class, called Iterative Target Class Method [56]:}
\begin{equation}
  \begin{gathered}
      I_0^{adv} = I,\\
      I_{N+1}^{adv} = Clip_{I, \epsilon}\left\{I_N^{adv}-\epsilon \cdot \text{ sign}(\nabla_I J(I_N^{adv},y_{target}))\right\}.
  \end{gathered}
\end{equation}

@@

\textbf{We have replaced ``We adopt COCO [63], ILSVRC-VID [64] and the training splits of GOT-10k [12] and LaSOT [13] as our training set. (see Table I)'' with}
``\uline{We adopt COCO [63], ILSVRC-VID [64] and the training splits of GOT-10k [12] and LaSOT [13] as our training set.}''
\textbf{in Section IV.B of the revised manuscript.}

\textit{8. Missing key ref : "Deep Learning for Visual Tracking: A Comprehensive Survey," in IEEE Transactions on Intelligent Transportation Systems, 2021.}

\textbf{Thanks for the good comment. We have cited this paper at Section II of the revised manuscript.  For your convenience in cross-checking, the new text is given as follows.}

\uline{A comprehensive survey of the related trackers is beyond the scope of this paper, please refer to [25] for a thorough survey.}

@@

\textbf{Many thanks for your positive comments on the strength of our paper and the novelty of the proposed attack method.}

\textit{My major concern is that the writing and organization need to be carefully modified and optimized. Besides, 1. Authors are focused on the anchor-free tracker in the experiments, but the anchor-free Siamese trackers are not well mentioned. I suggest the authors to include the discussion of state-of-the-art of other similar approaches (e.g., FCOT, SiamCAR, OCEAN, et. al.).}

\textbf{We have discussed several state-of-the-art anchor free Siamese trackers at the related work. For your convenience of cross review, the new text is given as follows.}

\uline{In this anchor-free paradigm, many recent works (e.g., [20], [21], [22]) are dedicated to more robust and efficient visual tracking based on various anchor-free settings.
% Ocean
Ocean [20] directly predicts the position and scale of target objects in an anchor-free fashion; since each sample position in groundtruth boxes is well trained, the tracker is capable of rectifying inexact predictions of target objects during inference.
% FCOT
FCOT [21] introduces an online regression model generator (RMG) based on the carefully designed anchor-free box regression branch, which enables the tracker to be more effective in handling target deformation during tracking procedure.
%  SiamCAR
SiamCAR [22] is both anchor and proposal free, and takes one unique response map to predict object location and bounding box directly; this setting significantly reduces the number of hyper-parameters, which keeps the tracker from complicated parameter tuning and makes the tracker significantly simpler, especially in training.
}

@@

\textit{2. The model is trained based on Eq.11 and Eq.12. It is not clear why the sign function is introduced. It is also suggested to describe the derivation of these two equations in detail.}

\textbf{Thanks for the good comment. As suggested, we have explained in detail the perturbation update process in offline training.
The detailed analysis is added in Section III.B of the revised manuscript.
For your convenience in cross-checking, the new text is given as follows.}

\uline{Before introducing our perturbation update process in offline training, we first revisit the popular adversarial example generation methods (\eg,~[55], [56]). One of the simplest methods to generate adversarial image $I^{adv}$ is FGSM~[55] and works by linearizing the loss function around the network weights and obtaining an optimal max-norm constrained perturbation for generating the adversarial image:}
\begin{equation}
    I^{adv} = I + \epsilon \cdot \text{ sign} \bigl( \nabla_I J(I, y_{true})  \bigr),
    \vspace{-0.1cm}
\end{equation}
\uline{where $I$ is the input clean image, and the values of its pixels are integer numbers in the range [0, 255]. $y_{true}$ is the true label for the image $I$, $J(I, y_{true})$ is the cost function for training the neural network, and $\epsilon$ is a hyper-parameter to be chosen. A straightforward way to extend the above method is applying it multiple times with small step size. This leads to Basic Iterative Method (BIM) introduced in [56]:}
\begin{equation}
    \begin{gathered}
        I_0^{adv} = I, \\
        I_{N+1}^{adv} = Clip_{I, \epsilon}\left\{I_N^{adv}+\epsilon \cdot \text{ sign}(\nabla_I J(I_N^{adv},y_{true}))\right\},
    \end{gathered}
\end{equation}
\uline{where the pixel values of intermediate results are clipped after each step to ensure that they are in
an $\epsilon$-neighbourhood of the original image. The BIM method can be easily made into an attacker for a specific desired target class, called Iterative Target Class Method [56]:}
\begin{equation}
  \begin{gathered}
      I_0^{adv} = I,\\
      I_{N+1}^{adv} = Clip_{I, \epsilon}\left\{I_N^{adv}-\epsilon \cdot \text{ sign}(\nabla_I J(I_N^{adv},y_{target}))\right\}.
  \end{gathered}
  \label{equ:itcm}
\end{equation}

@@

\textbf{Thanks for the good comment. We have unified the format of all the Tables in the revised manuscript.}

\textit{4. There are many typos in the paper, including but not limited to the following errors:}

\textit{(a) In the third line below Eq.7, $A_{a}dd$ should be $A_{add}$.}

\textit{(b) In page 2, difference datasets GOT-10K[12], LaSOT [12] cite the same reference.}

@@

\textbf{We have replaced ``In SiamFC++, the tracker first transforms the paired reference frame $I_1$ and annotation $b_1^{gt}$ to get an template image $\textbf z_1$, and transforms the search frame $I_i$ to get the search image $\textbf x_i$ centered at the position estimated in the previous frame.'' with}
``\uline{In SiamFC++, the tracker first transforms the paired reference frame $I_1$ and annotation $b_1^{gt}$ to get a template image $\textbf z_1$, and transforms the search frame $I_i$ to get the search image $\textbf x_i$ centered at the position estimated in the previous frame.}''
\textbf{in Section III.A of the revised manuscript.}

\textbf{We have replaced ``However, CNN attacks are usually expected imperceptible but the above method has to paste an obviously noticeable fake target patch to tracking frames, which raises the risk of being suspected.'' with}
``\uline{However, CNN attacks are usually expected to be imperceptible but the above method has to paste an obviously noticeable fake target patch to tracking frames, which raises the risk of being suspected.}''
\textbf{in Section III.A of the revised manuscript.}

\textbf{We have  replaced ``$A_add$ adds the patch into the search image $\textbf x$ at location $(\frac{x_0+x_1}{2},\frac{y_0+y_1}{2})$.'' with}
``\uline{$A_{add}$ adds the patch into the search image $\textbf x$ at location $(\frac{x_0+x_1}{2},\frac{y_0+y_1}{2})$.}''
\textbf{in Section III.B of the revised manuscript.}

\textbf{We have replaced ``We evaluate our video-agnostic perturbations for targeted attacks on several tracking benchmarks, i.e., OTB2015 [11], GOT-10k [12], LaSOT [13], UAV123 [13], VOT1016 [14], VOT2018 [15] and VOT2019 [16].'' with}
``\uline{We evaluate our video-agnostic perturbations for targeted attacks on several tracking benchmarks, i.e., OTB2015 [11], GOT-10k [12], LaSOT [13], VOT2016 [14], VOT2018 [15] and VOT2019 [16].}''
\textbf{in Section IV.A of the revised manuscript.}

\textbf{We have replaced ``We adopt COCO [63], ILSVRC-VID [64] and the training splits of GOT-10k [12] and LaSOT [13] as our training set. (see Table I)'' with}
``\uline{We adopt COCO [63], ILSVRC-VID [64] and the training splits of GOT-10k [12] and LaSOT [13] as our training set.}''
\textbf{in Section IV.B of the revised manuscript.}

%\normalem
% \bibliographystyle{IEEEtran}
% \bibliography{ref.bib}

### 2021-09-27 博士/论文提交/adversarial_attack/TCSVT/大修/response/response.tex

\textbf{Many thanks for your positive comments on the strength of our paper and the novelty of the proposed attack method.}

%%%% 问题 1.1 %%%%
\textit{In addition, I suggest the authors add more experiments to demonstrate the practicability of the attack method when the ground truth box information is missing in the training data. The experimental results show that it is effective to use the predicted boxes instead of ground truth boxes for training perturbations.}

\textbf{Thanks for the good comment. As suggessted, we have added more experiments to demonstrate the practicability of the attack method when the ground truth box information is missing in the training data. Specifically, we evaluate the untargeted and targeted attack performance using the following metrics on specific datasets: (1) AO and Precision on OTB2015, (2) SR and AO on GOT-Val, and (3) Precision, Normalized Precision and AO on LaSOT. The detailed analysis of new added experiments is added in Section IV.E of the revised manuscript. For your convenience in cross-checking, the new text is given as follows.}

### 2021-09-27 博士/论文提交/adversarial_attack/TCSVT/大修/response/response.tex

\textit{- On page 4, ‘imperceptible’ $\rightarrow$ ‘imperceptibly’ in line 57.}

\textit{- The reinitialization of VOT-toolkit should be mentioned in the part of ‘experimental setup’.}

\textit{- On page 7, ‘.(see Table I)’ is a typo.}

\textbf{Thanks for the good comment. We have carefully checked through the whole text and corrected the grammar mistakes and typos. Specifically,}
\textbf{We have replaced ``Experiment results on OTB2015 [11], GOT-10k [12], LaSOT [12], UAV123 [13], VOT1016 [14], VOT2018 [15] and VOT2019 [16]. benchmarks demonstrate the effectiveness and efficiency of our approach.'' with}
``\uline{Experiment results on OTB2015 [11], GOT-10k [12], LaSOT [13], VOT2016 [14], VOT2018 [15] and VOT2019 [16] benchmarks have demonstrated the effectiveness and efficiency of our approach.}''
\textbf{in Section I of the revised manuscript.}

### 2021-09-27 博士/论文提交/adversarial_attack/TCSVT/大修/response/response.tex

\textit{- The reinitialization of VOT-toolkit should be mentioned in the part of ‘experimental setup’.}

\textit{- On page 7, ‘.(see Table I)’ is a typo.}

\textbf{Thanks for the good comment. We have carefully checked through the whole text and corrected the grammar mistakes and typos. Specifically,}
\textbf{We have replaced ``Experiment results on OTB2015 [11], GOT-10k [12], LaSOT [12], UAV123 [13], VOT1016 [14], VOT2018 [15] and VOT2019 [16]. benchmarks demonstrate the effectiveness and efficiency of our approach.'' with}
``\uline{Experiment results on OTB2015 [11], GOT-10k [12], LaSOT [13], VOT2016 [14], VOT2018 [15] and VOT2019 [16] benchmarks have demonstrated the effectiveness and efficiency of our approach.}''
\textbf{in Section I of the revised manuscript.}

\textbf{We have added the definition of $b_{\textbf{x}}^{fake}$ of Eq.4 as follows:}
``\uline{$b_{\textbf{x}}^{fake} = \{x_0, y_0, x_1, y_1\}$ denotes the coordinates of the upper-left and lower-right corners of the fake target on the search image.}''
\textbf{in Section III.A of the revised manuscript.}

### 2021-09-27 博士/论文提交/adversarial_attack/TCSVT/大修/response/response.tex

\textbf{Thanks for the good comment. We have carefully checked through the whole text and corrected the grammar mistakes and typos. Specifically,}
\textbf{We have replaced ``Experiment results on OTB2015 [11], GOT-10k [12], LaSOT [12], UAV123 [13], VOT1016 [14], VOT2018 [15] and VOT2019 [16]. benchmarks demonstrate the effectiveness and efficiency of our approach.'' with}
``\uline{Experiment results on OTB2015 [11], GOT-10k [12], LaSOT [13], VOT2016 [14], VOT2018 [15] and VOT2019 [16] benchmarks have demonstrated the effectiveness and efficiency of our approach.}''
\textbf{in Section I of the revised manuscript.}

\textbf{We have added the definition of $b_{\textbf{x}}^{fake}$ of Eq.4 as follows:}
``\uline{$b_{\textbf{x}}^{fake} = \{x_0, y_0, x_1, y_1\}$ denotes the coordinates of the upper-left and lower-right corners of the fake target on the search image.}''
\textbf{in Section III.A of the revised manuscript.}

\textbf{We have replaced ``In SiamFC++, the tracker first transforms the paired reference frame $I_1$ and annotation $b_1^{gt}$ to get an template image $\textbf z_1$, and transforms the search frame $I_i$ to get the search image $\textbf x_i$ centered at the position estimated in the previous frame.'' with}
``\uline{In SiamFC++, the tracker first transforms the paired reference frame $I_1$ and annotation $b_1^{gt}$ to get a template image $\textbf z_1$, and transforms the search frame $I_i$ to get the search image $\textbf x_i$ centered at the position estimated in the previous frame.}''
\textbf{in Section III.A of the revised manuscript.}

\textbf{We have replaced ``However, CNN attacks are usually expected imperceptible but the above method has to paste an obviously noticeable fake target patch to tracking frames, which raises the risk of being suspected.'' with}
``\uline{However, CNN attacks are usually expected to be imperceptible whereas the above method has to paste an obviously noticeable \textit{fake target} patch into tracking frames, which raises the risk of being suspected.}''
\textbf{in Section III.A of the revised manuscript.}

### 2021-09-27 博士/论文提交/adversarial_attack/TCSVT/大修/response/response.tex

\textbf{We have replaced ``In SiamFC++, the tracker first transforms the paired reference frame $I_1$ and annotation $b_1^{gt}$ to get an template image $\textbf z_1$, and transforms the search frame $I_i$ to get the search image $\textbf x_i$ centered at the position estimated in the previous frame.'' with}
``\uline{In SiamFC++, the tracker first transforms the paired reference frame $I_1$ and annotation $b_1^{gt}$ to get a template image $\textbf z_1$, and transforms the search frame $I_i$ to get the search image $\textbf x_i$ centered at the position estimated in the previous frame.}''
\textbf{in Section III.A of the revised manuscript.}

\textbf{We have replaced ``However, CNN attacks are usually expected imperceptible but the above method has to paste an obviously noticeable fake target patch to tracking frames, which raises the risk of being suspected.'' with}
``\uline{However, CNN attacks are usually expected to be imperceptible whereas the above method has to paste an obviously noticeable \textit{fake target} patch into tracking frames, which raises the risk of being suspected.}''
\textbf{in Section III.A of the revised manuscript.}

\textbf{We have  replaced ``$A_add$ adds the patch into the search image $\textbf x$ at location $(\frac{x_0+x_1}{2},\frac{y_0+y_1}{2})$.'' with}
``\uline{$A_{add}$ adds the patch into the search image $\textbf x$ at location $(\frac{x_0+x_1}{2},\frac{y_0+y_1}{2})$.}''
\textbf{in Section III.B of the revised manuscript.}

\textbf{We have replaced ``We evaluate our video-agnostic perturbations for targeted attacks on several tracking benchmarks, i.e., OTB2015 [11], GOT-10k [12], LaSOT [13], UAV123 [13], VOT1016 [14], VOT2018 [15] and VOT2019 [16].'' with}
``\uline{We evaluate our video-agnostic perturbation method for targeted attacks on several tracking benchmarks, i.e., OTB2015 [11], GOT-10k [12], LaSOT [13], VOT2016 [14], VOT2018 [15] and VOT2019 [16].}''
\textbf{in Section IV.A of the revised manuscript.}

### 2021-09-27 博士/论文提交/adversarial_attack/TCSVT/大修/response/response.tex

%%%% 问题 3.2 %%%%
\textit{2. The proposed method and offline training phase should be explained more clearly. For instance, the termination of offline training or offline optimization is missed affecting perturbation values.}

\textbf{Thanks for the good comment. As suggested, we have explained in detail the perturbation update process in offline training.
The detailed analysis is added in Section III.B of the revised manuscript.
For your convenience in cross-checking, the new text is given as follows.}

\uline{Before introducing our perturbation update process in offline training, we first revisit the popular adversarial example generation methods (\eg,~[55], [56]). One of the simplest methods to generate adversarial image $I^{adv}$ is FGSM~[55] and works by linearizing the loss function around the network weights and obtaining an optimal max-norm constrained perturbation for generating the adversarial image:}
\begin{equation}
    \renewcommand\theequation{11}
    I^{adv} = I + \epsilon \cdot \text{ sign} \bigl( \nabla_I J(I, y_{true})  \bigr),
    \vspace{-0.1cm}
\end{equation}
\uline{where $I$ is the input clean image, and the values of its pixels are integer numbers in the range [0, 255]. $y_{true}$ is the true label for the image $I$, $J(I, y_{true})$ is the cost function for training the neural network, and $\epsilon$ is a hyper-parameter to be chosen. A straightforward way to extend the above method is applying it multiple times with small step size. This leads to Basic Iterative Method (BIM) introduced in [56]:}
\begin{equation}
  \renewcommand\theequation{12}
    \begin{gathered}
        I_0^{adv} = I, \\
        I_{N+1}^{adv} = Clip_{I, \epsilon}\left\{I_N^{adv}+\epsilon \cdot \text{ sign}(\nabla_I J(I_N^{adv},y_{true}))\right\},
    \end{gathered}
\end{equation}
\uline{where the pixel values of intermediate results are clipped after each step to ensure that they are in
an $\epsilon$-neighbourhood of the original image. The BIM method can be easily made into an attacker for a specific desired target class, called Iterative Target Class Method [56]:}
\begin{equation}
  \renewcommand\theequation{13}
  \begin{gathered}
      I_0^{adv} = I,\\
      I_{N+1}^{adv} = Clip_{I, \epsilon}\left\{I_N^{adv}-\epsilon \cdot \text{ sign}(\nabla_I J(I_N^{adv},y_{target}))\right\}.
  \end{gathered}
\end{equation}

\uline{We utilize this Iterative Target Class Method to update our perturbation values during the training process. To achieve a balance between the attack efﬁciency and the perturbation perceptibility, we constrain the perturbation values in the loss function of Eq.~(10) instead of using the clip operation. At each training step, our perturbations are updated as follows:}
\begin{equation}
\renewcommand\theequation{14}
\delta_{k+1} = \delta_{k} - \epsilon_1 \cdot \text{sign}(\nabla_{\delta_k}L)
\end{equation}
\begin{equation}
\renewcommand\theequation{15}
p_{k+1} = p_{k} - \epsilon_2 \cdot \text{sign}(\nabla_{p_k}L),
\end{equation}

@@

% figure 4
\textbf{In Figure 4, we have replaced ``Results of targeted attacks where the tracker is forced to follow a predefined \textit{fake trajectory} (indicated by the yellow targeted bounding box).'' with}
\uline{``Results of targeted attacks where the tracker is forced to follow a predefined \textit{fake trajectory} $B^{fake}=\{b^{fake}_i\}_1^{T}$ (indicated by the yellow bounding boxes). The \textit{fake trajectory} follows the real trajectory $B^{gt}=\{b^{gt}_i\}_1^T$ (indicated by the red bounding boxes) except that the adjacent boundaries of $b^{fake}_i$ and $b^{gt}_i$ are 2 pixels apart.''}

\textit{4. I suggest adding the advantages \& limitations of the proposed method after experimental analysis and future works to the conclusion.}

\textbf{Thanks for the good commenet. As suggested, we have added the advantages \& limitations of the proposed method after experimental analysis and future works to the conclusion. For your convenience in cross-checking, the new text is given as follows.}

\uline{In summary, compared with other attack methods, our method has two key advantages. First, the proposed attack method only needs to perform the addition operations to deploy the adversarial information for any novel video without gradient optimization or network inference, making it possible to attack a real-world online-tracking system when we can not get access to the limited computational resources. Second, the proposed perturbations show good transferability to other anchor-free or anchor-based trackers. The main limitation of our work is that the translucent perturbations my result in suspicious attacks.
In the future work, we expect that it will be possible to further reduce the possible suspicion by increasing the perturbation's imperceptibility while maintaining the attack efficiency.}

@@

\textit{2. The model is trained based on Eq.11 and Eq.12. It is not clear why the sign function is introduced. It is also suggested to describe the derivation of these two equations in detail.}

\textbf{Thanks for the good comment. As suggested, we have explained in detail the perturbation update process in offline training.
The detailed analysis is added in Section III.B of the revised manuscript.
For your convenience in cross-checking, the new text is given as follows.}

\uline{Before introducing our perturbation update process in offline training, we first revisit the popular adversarial example generation methods (\eg,~[55], [56]). One of the simplest methods to generate adversarial image $I^{adv}$ is FGSM~[55] and works by linearizing the loss function around the network weights and obtaining an optimal max-norm constrained perturbation for generating the adversarial image:}
\begin{equation}
    \renewcommand\theequation{11}
    I^{adv} = I + \epsilon \cdot \text{ sign} \bigl( \nabla_I J(I, y_{true})  \bigr),
    \vspace{-0.1cm}
\end{equation}
\uline{where $I$ is the input clean image, and the values of its pixels are integer numbers in the range [0, 255]. $y_{true}$ is the true label for the image $I$, $J(I, y_{true})$ is the cost function for training the neural network, and $\epsilon$ is a hyper-parameter to be chosen. A straightforward way to extend the above method is applying it multiple times with small step size. This leads to Basic Iterative Method (BIM) introduced in [56]:}
\begin{equation}
    \renewcommand\theequation{12}
    \begin{gathered}
        I_0^{adv} = I, \\
        I_{N+1}^{adv} = Clip_{I, \epsilon}\left\{I_N^{adv}+\epsilon \cdot \text{ sign}(\nabla_I J(I_N^{adv},y_{true}))\right\},
    \end{gathered}
\end{equation}
\uline{where the pixel values of intermediate results are clipped after each step to ensure that they are in
an $\epsilon$-neighbourhood of the original image. The BIM method can be easily made into an attacker for a specific desired target class, called Iterative Target Class Method [56]:}
\begin{equation}
  \renewcommand\theequation{13}
  \begin{gathered}
      I_0^{adv} = I,\\
      I_{N+1}^{adv} = Clip_{I, \epsilon}\left\{I_N^{adv}-\epsilon \cdot \text{ sign}(\nabla_I J(I_N^{adv},y_{target}))\right\}.
  \end{gathered}
  \label{equ:itcm}
\end{equation}

\uline{We utilize this Iterative Target Class Method to update our perturbation values during the training process. To achieve a balance between the attack efﬁciency and the perturbation perceptibility, we constrain the perturbation values in the loss function of Eq.~(10) instead of using the clip operation. At each training step, our perturbations are updated as follows:}
\begin{equation}
  \renewcommand\theequation{14}
  \delta_{k+1} = \delta_{k} - \epsilon_1 \cdot \text{sign}(\nabla_{\delta_k}L)
  \end{equation}
  \begin{equation}
  \renewcommand\theequation{15}
  p_{k+1} = p_{k} - \epsilon_2 \cdot \text{sign}(\nabla_{p_k}L),
\end{equation}
